---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cpss

<!-- badges: start -->
<!-- badges: end -->

Change-Point Detection by Sample-Splitting Methods.

## Installation

You can install the released version of cpss from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("cpss")
```

Or the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ghwang-nk/cpss")
```

## Getting started

It is easy to get started with the cpss.* set of functions by accessing their documentation pages (e.g., ?cpss).

```{r example}
library(cpss)
?cpss.mean
?cpss.var
?cpss.meanvar
?cpss.glm
?cpss.lm
?cpss.em
?cpss.custom
```

## References

1. Zou, C., Wang, G., and Li, R. (2020) Consistent selection of the number of change-points via sample-splitting. The Annals of Statistics, 48, 413–439.

1. Wang, G., and Zou, C. (2022+) cpss: An R package for change-point detection by sample-splitting methods. To appear in Journal of Quality Technology.
